TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-20 paper/draft.tex
add acknowledgments'

The final selection for our ``safe'' is displayed in Figure \ref{fig:safe_selection}. We also note that applying our model requires very little computational demand: the time to run a model on all 14,827 sources was two minutes on a personal laptop.

JB: NOW POINT TO RESULTS FIGURES AND SUMMARIZE THEM, IF THERE IS ANYTHING ELSE?

@@

%%==========================================================================================
\acknowledgements
We would like to acknowledge Hans Walter Rix (MPIA), Derek Homeier (Universit{\"a}t Heidelberg), Wolfgang Bradner (MPIA), Anna-Christina Eilers (MPIA) for constructive discussions in the process of this project, as well as Bertrand Goldman (MPIA) and those who have supported the internship program at the Max Planck Institute f{\"u}r Astronomie for providing JB with funding and hospitality.

>>>>

The three panels of \ref{fig:safe_selection} show before and after selection of the sources in \gaia\ color-magnitude space, colored by \thecannon\ determined temperatures, metallicities, and spectral types, with their respective training samples overplotted in orange. Comparisons between the West-trained spectral types and Mann-trained temperatures and metallicities are shown in Figure \ref{fig:west_vs_mann}: left shows the slight negative correlation between spectral type and [Fe/H], and right shows the nonlinear decrease in temperature with visible metallicity gradient. We also note that applying our model requires very little computational demand: the time to train and test a model on all 14,827 sources was two minutes on a personal laptop.

% JB: NOW POINT TO RESULTS FIGURES AND SUMMARIZE THEM, IF THERE IS ANYTHING ELSE?

@@

%%==========================================================================================
\acknowledgements
We would like to acknowledge Hans Walter Rix (MPIA), Derek Homeier (Universit{\"a}t Heidelberg), Wolfgang Bradner (MPIA), Anna-Christina Eilers (MPIA), Diogo Souto (Observatário Nacional/MCTI) and Keivan Stassun (Vanderbuilt) for constructive discussions in the process of this project, as well as Bertrand Goldman (MPIA) and those who have supported the internship program at the Max Planck Institute f{\"u}r Astronomie for providing JB with funding and hospitality.
